Association between trauma severity models and opportunities for improvement: A retrospective cohort study

### 2022-09-15 manuscript.Rmd
making a test table one

---
title: "Association between trauma severity models and opportunities for improvement"
author: "Victoria Witthoff"
output:
  pdf_document: default
  html_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

<!-- This is an R Markdown document. Markdown is a simple formatting
syntax for authoring HTML, PDF, and MS Word documents. For more
details on using R Markdown see http://rmarkdown.rstudio.com -->

<!-- This is a comment and will not be present in the compiled
document. Try "knitting" this document by clicking the knit button up
to the left, or by running `rmarkdown::render("manuscript.Rmd")` in
the console and you should only see headings -->

<!-- Structure and most comments are from the Strengthening the
reporting of observational studies in epidemiology (STROBE) statement,
see https://www.strobe-statement.org/. For more explanations see the
paper Strengthening the Reporting of Observational Studies in
Epidemiology (STROBE):explanation and elaboration.  -->

<!-- Indicate the study’s design with a commonly used term in the
title, for example: "Associations between resuscitation interventions
and opportunities for improvement in adult trauma patients: A cohort
study" -->

@@

You can cite document here like this [@exampleKey9999]. Open the file
bibliography.bib to learn more.

@@

You can include code in this document like this:

```{r main, echo=FALSE}
## source("main.R") ## This "imports" the main script file of your project and run any code in it
```

You can also embed plots:

```{r plot, echo=FALSE}
plot(pressure)
```

You can also mix text and code, so called inline code, like this: `r 2+5`.

@@

<!-- Do not edit by hand, references will be inserted and formatted automatically once you knit this document -->

>>>>

---
title: "Association between trauma severity models and opportunities for improvement: A retrospective cohort study"
author: "Victoria Witthoff"
output:
  pdf_document: default
  html_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

@@

@@

```{r main, echo=FALSE, message = FALSE}
  source("main.R") ## This "imports" the main script file of your project and run any code in it
  as.data.frame(t1)
```

@@
